Local-global principle for $\K_2$ of Chevalley groups

### 2015-09-30 paper.tex
Added a passage removed from JPAA article

The next step of the proof is to is construct certain elements in $\St(n, R)$ which are similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.

Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.
\begin{lemma}
 Let $u, v \in R^n$ be columns such that $v^t \cdot u = 0$ and there exists $w = w(u) \in R^n$ satisfying $w^t \cdot u = a^N$ for some natural number $N$.
 In this context one can define certain elements $Z^{1}(u,v), Z^{2}(v, u)$ of $\St(n, R)$. These elements satisfy the following relations:
 \begin{itemize}
  \item $Z^{1}(u, v_1 + v_2) = Z^{1}(u, v_1) \cdot Z^{1}(u, v_2)$;
  \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$.
 \end{itemize}
\end{lemma}
\begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}

>>>>

The next step of the proof is to is construct certain elements in $\St(n, R)$ similar to Tulenbaev's elements $X_{u,v}(a)$ see~\cite[\S~1]{T}.

Assume that $n \geq 4$. For the rest of this section $a$ denotes a nonnilpotent element of $R$.

Let $v\in R^n$ be a column.
A column $w\in R^n$ is called \emph{$v$-decomposable} if it can be presented as a finite sum $w = \sum\limits_{i=1}^n w^i$ of columns such that each $w^i$ 
has at least two zero entries. 
Denote by $D(v)$ the submodule of $R^n$ consisting of all $v$-decomposable columns.
%For a column $v\in R^n$ denote by $I(v)$ the ideal of $R$ spanned by coordinates $v_1,\ldots, v_n$.

Let $u,v,w\in R^n$ be columns such that $w^tv=0$.
It is easy to check that $(uv)\cdot w = \sum_{i<j}w_{ij}$, where $w_{ij} = (w_iu_j - w_ju_i)(v_je_i - v_ie_j)\in{}\!A^n$ (cf.~\cite[Lemma~3.2]{Ka}).
Such decomposition is called the {\it canonical} decomposition of $(uv)\cdot w$.
In particular, this shows that row $a\cdot w$ is always $v$-decomposable for $a\in I(v)$, i.e. $I(v) \cdot O(v) \subseteq D(v)$.
It is also obvious that $O(v)\subseteq O(bv)$, $D(v)\subseteq D(bv)$ for $b \in R$.

Let $v$ be a (not neccessarily unimodular) column of height $n$, let $w$ be a $v$-decomposable row and $a$ be an element of $I(v)$.
In this context Tulenbaev defines elements $X_{v,w}(a)$ of the Steinberg group $\St(n, A)$, $n\geq 4$ (see~\cite[\S~1]{T}).
Tulenbaev requires $a \in I(v)$ in order to prove correctness of his definition.

Let us list certain useful properties of these elements.
\begin{lemma}\label{T13} Let $n\geq 4$. Elements $X_{v,w}(a)$ satisfy the following relations:
\begin{enumerate}
 \item $X_{v, w}(ab) = X_{v, bw}(a)$ for $w\in D(v)$, $b\in R$, $a\in I(v)$. If moreover $a\in b \cdot I(v)$ then $X_{v, w}(ab) = X_{bv, w}(a)$.
 \item $X_{v,w_1 + w_2}(a) = X_{v, w_1}(a) X_{v, w_2}(a)$, $w_1, w_2 \in D(v)$, $a\in I(v)$.
 \item \label{T133} For $g\in\St(n, A)$,  $w\in O(v)$, $a,b\in I(v)$  one has  $g^{-1}\cdot X_{v, bw}(a)\cdot g = X_{g^{-1}v, bwg}(a)$
 \item Let $a$ be a nonnilpotent element of $A$.
       For $n\geq 5$ let $(v_1,v_2)\in M_{n\times 2}(A)$ be a matrix such that its image in $M_{n\times 2}(A_a)$ is unimodular.
       Let $w \in {}^n\!A$ be a row such that $wv_1=wv_2=0$. Then for sufficiently large natural numbers $k, m$ one has
       $$X_{v_1 + bv_2, a^kw}(a^m) = X_{v_1,a^kw}(a^m)\cdot X_{v_2,ba^kw}(a^m),\ b\in A.$$
\end{enumerate}\end{lemma}

\begin{lemma}
 Let $u, v \in R^n$ be columns such that $v^t \cdot u = 0$ and there exists $w = w(u) \in R^n$ satisfying $w^t \cdot u = a^N$ for some natural number $N$.
 In this context one can define certain elements $Z^{1}(u,v), Z^{2}(v, u)$ of $\St(n, R)$. These elements satisfy the following relations:
 \begin{itemize}
  \item $Z^{1}(u, v_1 + v_2) = Z^{1}(u, v_1) \cdot Z^{1}(u, v_2)$;
  \item $Z^{2}(v_1 + v_2, u) = Z^{2}(v_1, u) \cdot Z^{2}(v_2, u)$;
  \item ${}^{g}\! Z^{\tau}(u, v) = Z^{\tau}(g \cdot u, g^* \cdot v)$, $\tau = 1..2$, $g \in \St(n, R)$.
 \end{itemize}
\end{lemma}
\begin{proof} Both the construction of $Z^i$ and the relations for $Z^i$ are, in essence, just~\cite[Lemma~1.3]{T} applied twice. \end{proof}
